---
title: "2.1_imputation_cohort1"
author: "Judith Gilsbach"
date: "2023-12-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages
```{r}
library(haven)
library(tidyverse)
library(tidygraph)
library(network)
library(igraph)
library(RSiena)
library(knitr)
library(tableHTML)
library(stargazer)
```

# Load environment from initial setup
```{r}
#load cleaned data
```


# Define helper functions

```{r}
#Define Function that will hopefully ensure convergence in RSiena (this is from Siena Manual)
siena07ToConvergence <- function(alg, dat, eff, ans0 = NULL, threshold = 0.25,
                                 nodes = 1, ...){
  # parameters are:
  # alg, dat, eff: Arguments for siena07: algorithm, data, effects object.
  # ans0: previous answer, if available; used as prevAns in siena07.
  # threshold: largest satisfactory value
  #            for overall maximum convergence ratio (indicating convergence).
  # nodes: number of processes for parallel processing.
  if (!is.null(ans0)) {
    alg$nsub = 6
  }
  numr <- 0 # number of repetitions
  ans <- siena07(alg, data = dat, effects = eff, prevAns = ans0,
                 nbrNodes = nodes, returnDeps = TRUE,
                 useCluster = (nodes >= 2), ...) # the first run
  repeat {
    save(ans, file = paste("ans",numr,".RData",sep = "")) # to be safe
    numr <- numr + 1         # count number of repeated runs
    tm <- ans$tconv.max      # convergence indicator
    cat(numr, tm,"\n")       # report how far we are
    if (tm < threshold) {break}   # success
    if (tm > 10) {break}     # divergence without much hope
    # of returning to good parameter values
    if (numr > 20) {break}  # now it has lasted too long
    alg$nsub <- 1
    alg$n2start <- 2 * (sum(eff$include) + 7) * 2.52**4
    alg$n3 <- 3000
    if (numr == 1) {alg$firstg <- alg$firstg/5}
    ans <- siena07(alg, data = dat, effects = eff, prevAns = ans,
                   nbrNodes = nodes, returnDeps = TRUE,
                   useCluster = (nodes >= 2),...)
  }
  if (tm > threshold)
  {
    stop("Convergence inadequate.\n")
  }
  ans
}

#Since version 1.2-12, Maximum Likelihood (ML) estimation by Rsiena with returnDeps = TRUE returns an edgelist of the final network at the end of the phase 3 simulation.
#The following function, getNet(), uses this edgelist to impute the data.

getNet <- function(observedNet,edgeList) {
  # observedNet = observed network as adjacency with missing data
  # edgeList = edgelist that is returned by siena07(...)$sims
  observedNet[is.na(observedNet)] <- 0
  for (i in 1:nrow(edgeList)) {
    observedNet[edgeList[i,1],edgeList[i,2]] <- 1
  }
  return(observedNet)
}


```

# Imputation

All 63 students who started their freshman year in sociology in fall 2020 were invited to take part in the study but only 42 took part in the study (66 out of 83 for the 2nd cohort in fall 2021). We consider those as "taking part" who allowed us to take a photo of themselves or handed one in to be identified by their fellow students in the online survey and who additionally handed in the data protection agreement before the beginning of the field work of wave 1. 
Missing data occurred due to some students not taking part in all waves of the study. This missing data on the tie level shall be imputed because it does not only affect the knowledge about the missing actor but also about the other actors potentially nominated by the missing actor.


## Cohort 1 <br/>(2020/21)
### Defining the imputation model for the first wave

For  a detailed introduction to imputation using SAOM see the script prepared by Robert Krause: https://www.stats.ox.ac.uk/~snijders/siena/AdSUMMissingDataMD.html

```{r}
imp_W1_K1 <- list() #create list to store the imputed networks
D <- 50 #number of imputations

## Imputation with a stationary SAOM
relation_K1_full <- sienaDependent(array(c(relation_W1_K1_ma, relation_W1_K1_ma), dim = c(42, 42, 2)) ,
                          allowOnly = FALSE)

Female_v <- as.vector(Attributes_K1$Female)
Statistik_v <- as.vector(Attributes_K1$Statistik)
WiW_v <- as.vector(Attributes_K1$WiW)
both_tutorials_v <- as.vector(Attributes_K1$both_tutorials)

Female  <- coCovar(as.vector(Female_v),centered=FALSE)
Statistik  <- coCovar(as.vector(Statistik_v),centered=FALSE)
WiW  <- coCovar(as.vector(WiW_v),centered=FALSE)
both_tutorials  <- coCovar(as.vector(both_tutorials_v),centered=FALSE)
w2 <- coDyadCovar(relation_W2_K1_ma) #wave 1 is especially sparse, therefore wave 2 is used as a dyadic predictor
#eithertut <- coDyadCovar(either_tutorial_K1) #either WiW or Statistics tutorial group shared:only for appendix


Data.stationary <- sienaDataCreate(relation_K1_full,Statistik,WiW, both_tutorials,w2, Female)
effects.stationary <- getEffects(Data.stationary)
effects.stationary <- includeEffects(effects.stationary, recip, density, outActSqrt,inPopSqrt, inActSqrt, outIso)

effects.stationary <- setEffect(effects.stationary, gwespFF, parameter = 138)

effects.stationary <- setEffect(effects.stationary, outTrunc, parameter=2)

effects.stationary <- includeEffects(effects.stationary, sameX,
                                     interaction1 = "Statistik")
effects.stationary <- includeEffects(effects.stationary, sameX,
                                    interaction1 = "WiW")
effects.stationary <- includeEffects(effects.stationary, sameX,
                                     interaction1 = "both_tutorials")
effects.stationary <- includeEffects(effects.stationary, X, name = "relation_K1_full",
                                     interaction1 = "w2")
# effects.stationary <- includeEffects(effects.stationary, X, name = "relation_K1_full",
#                                      interaction1 = "eithertut")

#Gender
    effects.stationary <- includeEffects(effects.stationary,  sameX,
                                  interaction1 =  "Female")
    effects.stationary <- includeEffects(effects.stationary,  egoX,
                                  interaction1 =  "Female")
    effects.stationary <- includeEffects(effects.stationary,  altX,
                                  interaction1 =  "Female")

effects.stationary <- setEffect(effects.stationary, Rate, initialValue = 50,
                                name = "relation_K1_full", fix = TRUE, type = "rate")

#Now we can estimate the stationary SAOM with Methods of Moments (MoM) estimation. One converged estimate will suffice.

estimation.options <- sienaAlgorithmCreate(useStdInits = FALSE,
                                           seed = 2214,
                                           n3 = 1000, maxlike = FALSE,
                                           cond = FALSE) #n3 =number of datasets simulated

period0saom_K1 <- siena07ToConvergence(alg = estimation.options,
                                    dat = Data.stationary,
                                    eff = effects.stationary, threshold = 0.25)


#Now change the RSiena algorithm to impuatation

imputation.options <- sienaAlgorithmCreate(seed = 13848,
                                           useStdInits = FALSE, 
                                           maxlike = TRUE,
                                           cond = FALSE, 
                                           nsub = 0,
                                           simOnly = TRUE,
                                           n3 = 10)

######################## Goodness of fit should ideally be evaluated before using the model for imputation ###################

#Show results of the above model (the one that converged)
period0saom_K1
#t-ratio of the basic rate parameter is high and SE is NA, this is because the effect is fixed

#check for autocorrelation
period0saom_K1$ac

#t-statistics = parameter estimate divided by standard error, if they are bigger than 1.96 they are significant at the 0.05-level
significance <- ifelse((abs(period0saom_K1$theta/period0saom_K1$se)) > 1.96, TRUE, FALSE) #MIND: Absolute value
significance

#check for collinearity
summary(period0saom_K1)

```

### Imputing the first wave
```{r}
set.seed(142)
for (i in 1:D) {
  cat('imputation',i,'\n')
  
  n1 <- relation_W1_K1_ma
  n1 <- n1 + 10
  diag(n1) <- 0
  n2 <- n1
  tieList <- c(1:(nrow(n1)**2))[c(n1 == 11)]
  tieList <- tieList[!is.na(tieList)]
  
  changedTie <- sample(tieList,1)
  
  n1[changedTie] <- 0
  n2[changedTie] <- 1
  
  relation_K1_full <- sienaDependent(array(c(n1,n2), dim = c(42, 42, 2)),
                            allowOnly = FALSE )
  
  Data.stationary <- sienaDataCreate(relation_K1_full,Statistik, WiW, both_tutorials,w2, Female)

  
  sims <- siena07(imputation.options, data = Data.stationary,
                  effects = effects.stationary,
                  prevAns = period0saom_K1,
                  returnDeps = TRUE)$sims[[10]][[1]]
  
  imp_W1_K1[[i]] = getNet(relation_W1_K1_ma,sims)
  
}

```

### Imputing the later waves

```{r}
#create lists for the imputed networks of wave 2 and 3
imp_W2_K1 <- list()
imp_W3_K1 <- list()

#For each wave estimation is done With Method of Moments (MoM) and imputation with Maximum Likelihood (ML)
#Imputation is repeated as often as the first wave had been imputed (D times)

set.seed(1307)
for (i in 1:D) {
  
  cat('imputation',i,'\n')
  
  # now impute wave2
  
  relation_K1_full <- sienaDependent(array(c(imp_W1_K1[[i]],relation_W2_K1_ma),
                                  dim = c(42,42,2)))

  Data.w2  <- sienaDataCreate(relation_K1_full, Statistik, WiW, both_tutorials, Female)
  
  
  effects.twoWaves <- getEffects(Data.w2)
  effects.twoWaves <- includeEffects(effects.twoWaves,
                                     recip, density, outActSqrt, inPopSqrt, inActSqrt)
  
  effects.stationary <- setEffect(effects.stationary, gwespFF, parameter = 138)
  
  effects.twoWaves <- setEffect(effects.twoWaves, outTrunc, parameter=2)
  
  effects.twoWaves <- includeEffects(effects.twoWaves,  sameX,
                                     interaction1 = "Statistik")
  effects.twoWaves <- includeEffects(effects.twoWaves,  sameX,
                                     interaction1 = "WiW")
  effects.twoWaves <- includeEffects(effects.twoWaves,  sameX,
                                     interaction1 = "both_tutorials")
  # effects.twoWaves <- includeEffects(effects.twoWaves, X, name = "relation_K1_full",
  #                                    interaction1 = "eithertut")
  
  #Gender
  effects.twoWaves <- includeEffects(effects.twoWaves,  sameX,
                                  interaction1 =  "Female")
  effects.twoWaves <- includeEffects(effects.twoWaves,  egoX,
                                  interaction1 =  "Female")
  effects.twoWaves <- includeEffects(effects.twoWaves,  altX,
                                  interaction1 =  "Female")
  
  if (i == 1) {
    period1saom_K1 <- siena07ToConvergence(alg = estimation.options,
                                        dat = Data.w2,
                                        eff = effects.twoWaves,
                                        threshold = 0.25)
  } else {
    period1saom_K1 <- siena07ToConvergence(alg = estimation.options,
                                        dat = Data.w2,
                                        eff = effects.twoWaves,
                                        threshold = 0.25,
                                        ans0 = period1saom_K1)
  }
  
  sims <- siena07(imputation.options, data = Data.w2,
                  effects = effects.twoWaves,
                  prevAns = period1saom_K1,
                  returnDeps = TRUE)$sims[[10]][[1]]
  
  imp_W2_K1[[i]] <- getNet(relation_W2_K1_ma,sims)

########
  # impute wave 3
  
  relation_K1_full <- sienaDependent(array(c(imp_W2_K1[[i]], relation_W3_K1_ma),
                                   dim = c( 42, 42, 2)))
  Data.w3  <- sienaDataCreate(relation_K1_full, Statistik, WiW, both_tutorials, Female)
  
  if (i == 1) {
    period2saom_K1 <- siena07ToConvergence(alg = estimation.options,
                                        dat = Data.w3,
                                        eff = effects.twoWaves,
                                        threshold = 0.25)
  } else {
    period2saom_K1 <- siena07ToConvergence(alg = estimation.options,
                                        dat = Data.w3,
                                        eff = effects.twoWaves,
                                        threshold = 0.25,
                                        ans0 = period2saom_K1)
  }
  
  
  sims <- siena07(imputation.options, data = Data.w3,
                  effects = effects.twoWaves,
                  prevAns = period2saom_K1,
                  returnDeps = TRUE)$sims[[10]][[1]]
  
  imp_W3_K1[[i]] = getNet(relation_W3_K1_ma,sims)
  save.image('mi.RData') 
}

#check results:

period1saom_K1
period2saom_K1

summary(period1saom_K1)
summary(period2saom_K1)


#check for autocorrelation
period1saom_K1$ac
period2saom_K1$ac

#t-statistics = parameter estimate devided by standard error, if they are bigger than 1.96 they are significant at the 0.05-level
significance_p1_K1 <- ifelse((abs(period1saom_K1$theta/period1saom_K1$se)) > 1.96, TRUE, FALSE) #MIND: Absolute value
significance_p1_K1 
significance_p2_K1 <- ifelse((abs(period2saom_K1$theta/period2saom_K1$se)) > 1.96, TRUE, FALSE) #MIND: Absolute value
significance_p2_K1 

#check for collinearity
summary(period0saom_K1)
summary(period1saom_K1)
summary(period2saom_K1)
```


# Assessing _Goodness of Fit_ for the impuation models

## Cohort 1<br/>2020/21

```{r}
## Period 0
# 1: Goodness of Fit for the last imputation
saom.model_K1.results.gof <- list()
saom.model_K1.results.gof[[1]] <- plot(sienaGOF(period0saom_K1, varName="relation_K1_full", OutdegreeDistribution))
saom.model_K1.results.gof[[2]] <- plot(sienaGOF(period0saom_K1, varName="relation_K1_full", IndegreeDistribution))
#View results
saom.model_K1.results.gof[[1]] 
saom.model_K1.results.gof[[2]]

## Period 1
saom.model_K1.results.gof1 <- list()
saom.model_K1.results.gof1[[1]] <- plot(sienaGOF(period1saom_K1, varName="relation_K1_full", OutdegreeDistribution))
saom.model_K1.results.gof1[[2]] <- plot(sienaGOF(period1saom_K1, varName="relation_K1_full", IndegreeDistribution))
#View results
saom.model_K1.results.gof1[[1]] 
saom.model_K1.results.gof1[[2]]

## Period 2
saom.model_K1.results.gof2 <- list()
saom.model_K1.results.gof2[[1]] <- plot(sienaGOF(period2saom_K1, varName="relation_K1_full", OutdegreeDistribution))
saom.model_K1.results.gof2[[2]] <- plot(sienaGOF(period2saom_K1, varName="relation_K1_full", IndegreeDistribution))
#View results
saom.model_K1.results.gof2[[1]] 
saom.model_K1.results.gof2[[2]]

```

```{r}
todaysdate <- format(Sys.Date(),"%y%m%d")
save(list = ls(.GlobalEnv), file = paste0(todaysdate,"_imputation_cohort1_environment_",D,"imp.Rdata"))
```

```{r}
sessionInfo()
```