---
title: "4_cohort_comparison"
author: "Judith Gilsbach"
date: "2023-12-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages
```{r}
library(haven)
library(tidyverse)
library(tidygraph)
library(network)
library(igraph)
library(RSiena)
library(knitr)
library(tableHTML)
library(stargazer)
library(RColorBrewer)
library(gridExtra)
library(pals)
library(stringr)
library(plotrix)
library(ggsignif)
```

# Load environment from after imputation

## cohort 1 <br/>(2020/21)
```{r}
D <- 50 #number of imputations used in environment to load

#load analysis data for cohort one
```

## cohort 2 <br/>(2021/22)
```{r}
#load analysis data for cohort two
```

# Comparing cohorts according to RSiena manual

Testing the differences between the two cohorts by estimating a z-score and then a p-value for the parameter statistics being different from each other:

Test statistic (RSiena Manual, p. 105):

$\frac{\hat{\beta}_{K1}-\hat{\beta}_{K2}}{\sqrt{(s.e._{K1})^2 + (s.e._{K2})^2}}$

 
```{r}
#renaming effects
finalResults_rounded_K1$effect <- rownames(finalResults_K1)
finalResults_rounded_K2$effect <- rownames(finalResults_K1)



finalResults_rounded_compare <- full_join(finalResults_rounded_K1,finalResults_rounded_K2, by = "effect", suffix = c("_K1", "_K2"))
finalResults_rounded_compare$z_value <- (finalResults_rounded_compare$combinedEstimate_K1 - finalResults_rounded_compare$combinedEstimate_K2) /
                                              sqrt((finalResults_rounded_compare$combinedSE_K1)^2 + (finalResults_rounded_compare$combinedSE_K2)^2)
finalResults_rounded_compare$p_value <- round(pnorm(abs(finalResults_rounded_compare$z_value), mean = 0, sd = 1, lower.tail = F),3)

#print relevant columns
finalResults_rounded_compare[,c(5,1,2,6,7,10,11)]

#export
finalResults_rounded_compare_reduced <- finalResults_rounded_compare[,c(5,1,2,6,7,10,11)] %>% 
  mutate(est_se_K1 = paste0(as.character(format(round(combinedEstimate_K1,3)), nsmall = 3)," (",as.character(format(round(combinedSE_K1,3)), nsmall = 3),")"),
         est_se_K2 = paste0(as.character(format(round(combinedEstimate_K2,3)), nsmall = 3)," (",as.character(format(round(combinedSE_K2,3)), nsmall = 3),")"),
         p_value = as.character(format(round(p_value,3))),
         p_value = if_else(p_value == "0.000", "<.001", substr(p_value,2,5)),
         z_value = as.character(format(round(z_value,3)))) %>% 
  select(effect,est_se_K1,est_se_K2,z_value,p_value)



stargazer(finalResults_rounded_compare_reduced, summary = FALSE, title="Testing differences between cohorts",
          rownames = TRUE, type = "html", out = "Results/differences_K1_K2.html")

```

```{r}
#z-test for the within cohort comparison
rates <- as.data.frame(t(finalResults_rounded_compare %>% 
  filter(effect %in% c("constant relations_K1 rate (period 1)","constant relations_K1 rate (period 2)")) %>% 
  select(starts_with("combinedE")))) 

se <- as.data.frame(t(finalResults_rounded_compare %>% 
  filter(effect %in% c("constant relations_K1 rate (period 1)","constant relations_K1 rate (period 2)")) %>% 
  select(starts_with("combinedS"))))

rates_se <- cbind(rates,se)
colnames(rates_se) <- c("EstP1","EstP2","SEP1","SEP2")
rates_se <- rates_se %>% 
  mutate(z_value = (EstP1 - EstP2) / sqrt((SEP1)^2 + (SEP2)^2),
         p_value =round(pnorm(abs(z_value), mean = 0, sd = 1, lower.tail = F), digits = 4))
```

Differences between periods not significant in either cohort.

# Relative importance of effects
modelled according to Indlekofer and Brandes (2013), RSiena manual sec. 13.5.1

```{r}
# expectedRI: a list that contains the expected relative importances of effects aggregated over all actors for each network observation. These are the averages of the actor related values in RIActors. This is equation (4) in Indlekofer and Brandes (2013).

# cohort 1
#RI_K1 <-sienaRI(Data_K1, saomResults_K1[[1]]) 
#plot(RI_K1, addPieChart = T) # plot only for the first imputation



rel_importance_imp_w1_se_wi <- data.frame(matrix(nrow = 13,ncol = D))
rel_importance_imp_w2_se_wi <- data.frame(matrix(nrow = 13,ncol = D))
rel_importance_imp_w3_se_wi <- data.frame(matrix(nrow = 13,ncol = D))

rel_importance_impwise_w1 <- data.frame(matrix(nrow = 13,ncol = D))
rel_importance_impwise_w2 <- data.frame(matrix(nrow = 13,ncol = D))
rel_importance_impwise_w3 <- data.frame(matrix(nrow = 13,ncol = D))

for (i in 1:D) {
  if (i == 1) {
    
    RI_K1 <-sienaRI(Data_K1, saomResults_K1[[i]])
    #average expected relative importance over all actors summing over all imputations
    rel_importance_K1 <- as.matrix(as.data.frame(RI_K1$expectedRI, col.names = c("wave1","wave2","wave3")))
    
    #average expected relative importance over all actors by each imputation
    rel_importance_impwise_w1[,i] <- RI_K1$expectedRI[[1]]
    rel_importance_impwise_w2[,i] <- RI_K1$expectedRI[[2]]
    rel_importance_impwise_w3[,i] <- RI_K1$expectedRI[[3]]
    
    #relative importance of individual actor decisions
    rel_importance_actor_w1 <- as.matrix(as.data.frame(RI_K1$RIActors[[1]]))
    rel_importance_actor_w2 <- as.matrix(as.data.frame(RI_K1$RIActors[[2]]))
    rel_importance_actor_w3 <- as.matrix(as.data.frame(RI_K1$RIActors[[3]]))
    
    #within imputation standard error
    rel_importance_imp_w1_se_wi[,i] <- apply(as.data.frame(t(RI_K1$RIActors[[1]])),2, std.error) #std.error
    rel_importance_imp_w2_se_wi[,i] <- apply(as.data.frame(t(RI_K1$RIActors[[2]])),2, std.error) #std.error
    rel_importance_imp_w3_se_wi[,i] <- apply(as.data.frame(t(RI_K1$RIActors[[3]])),2, std.error) #std.error
    
  } else {
    
    RI_K1 <-sienaRI(Data_K1, saomResults_K1[[i]])
    #average expected relative importance over all actors; summing up over all imputations
    rel_importance_K1 <- rel_importance_K1 + as.matrix(as.data.frame(RI_K1$expectedRI, col.names = c("wave1","wave2","wave3")))
    
    #average expected relative importance over all actors by each imputation
    rel_importance_impwise_w1[,i] <- RI_K1$expectedRI[[1]]
    rel_importance_impwise_w2[,i] <- RI_K1$expectedRI[[2]]
    rel_importance_impwise_w3[,i] <- RI_K1$expectedRI[[3]]
    
    #relative importance of individual actor decisions; summing over all imputations
    rel_importance_actor_w1 <- rel_importance_actor_w1 + as.matrix(as.data.frame(RI_K1$RIActors[[1]]))
    rel_importance_actor_w2 <- rel_importance_actor_w2 + as.matrix(as.data.frame(RI_K1$RIActors[[2]]))
    rel_importance_actor_w3 <- rel_importance_actor_w3 + as.matrix(as.data.frame(RI_K1$RIActors[[3]]))
    
    #within imputation standard error
    rel_importance_imp_w1_se_wi[,i] <- apply(as.data.frame(t(RI_K1$RIActors[[1]])),2, std.error) #std.error
    rel_importance_imp_w2_se_wi[,i] <- apply(as.data.frame(t(RI_K1$RIActors[[2]])),2, std.error) #std.error
    rel_importance_imp_w3_se_wi[,i] <- apply(as.data.frame(t(RI_K1$RIActors[[3]])),2, std.error) #std.error
   
    
  }
}

rel_importance_imp_se_final <- data.frame(matrix(nrow = 13, ncol = 0))
rownames(rel_importance_imp_se_final) <- rownames(rel_importance_actor_w1)
#within imputation standard error: average over imputations
rel_importance_imp_se_final$w1_se_wi <- rowSums(rel_importance_imp_w1_se_wi^2)/D
rel_importance_imp_se_final$w2_se_wi <- rowSums(rel_importance_imp_w2_se_wi^2)/D
rel_importance_imp_se_final$w3_se_wi <- rowSums(rel_importance_imp_w3_se_wi^2)/D

#between imputation standard error
rel_importance_imp_w1_se_bi <- rowSums((rel_importance_impwise_w1 - rowMeans(rel_importance_impwise_w1))^2) / (D-1)
rel_importance_imp_w2_se_bi <- rowSums((rel_importance_impwise_w2 - rowMeans(rel_importance_impwise_w2))^2) / (D-1)
rel_importance_imp_w3_se_bi <- rowSums((rel_importance_impwise_w3 - rowMeans(rel_importance_impwise_w3))^2) / (D-1)

rel_importance_imp_se_final$w1_se_bi <- rel_importance_imp_w1_se_bi
rel_importance_imp_se_final$w2_se_bi <- rel_importance_imp_w2_se_bi
rel_importance_imp_se_final$w3_se_bi <- rel_importance_imp_w3_se_bi

#total standard error
rel_importance_imp_se_final$w1_se_total <- sqrt(rel_importance_imp_se_final$w1_se_wi + rel_importance_imp_se_final$w1_se_bi + (rel_importance_imp_se_final$w1_se_bi / D))
rel_importance_imp_se_final$w2_se_total <- sqrt(rel_importance_imp_se_final$w2_se_wi + rel_importance_imp_se_final$w2_se_bi + (rel_importance_imp_se_final$w2_se_bi / D))
rel_importance_imp_se_final$w3_se_total <- sqrt(rel_importance_imp_se_final$w3_se_wi + rel_importance_imp_se_final$w3_se_bi + (rel_importance_imp_se_final$w3_se_bi / D))

rel_importance_imp_se_final_K1 <- rel_importance_imp_se_final %>% 
  select(ends_with("total"))


rel_importance_K1 <- as.data.frame(rel_importance_K1/D)
rel_importance_K1$effect <- factor(c("outdegree (density)",
                                                        "reciprocity",
                                                        "triadic closure (GWESP FF, alpha =1.38)",
                                                        "indegree - popularity (sqrt)",
                                                        "indegree - activity (sqrt)",
                                                        "outdegree - activity (sqrt)",
                                                        "out-isolates (students nominating nobody)",
                                                        "same statistics tutorial group",
                                                        "same introduction to science tutorial group",
                                                        "both tutorial groups in common",
                                                        "female receiver",
                                                        "female sender",
                                                        "same gender")) #, levels = RI_K1$effectNames)
rel_importance_K1 <- rel_importance_K1 %>%
  pivot_longer(!effect, names_to = "wave", values_to = "size") %>% 
  mutate(effect = factor(effect, levels = as.character(unique(effect))))

rel_importance_actor_w1 <- as.data.frame(rel_importance_actor_w1/D) 
rel_importance_actor_w1$effect <- factor(c("outdegree (density)", "reciprocity", "triadic closure (GWESP FF, alpha =1.38)", "indegree - popularity (sqrt)",
                                           "indegree - activity (sqrt)", "outdegree - activity (sqrt)", "out-isolates (students nominating nobody)", "same statistics tutorial group",
                                           "same introduction to science tutorial group", "both tutorial groups in common", "female receiver", "female sender", "same gender")) #,
#levels = RI_K1$effectNames)
rel_importance_actor_w1 <- rel_importance_actor_w1 %>% 
  pivot_longer(!effect, names_to = "actor", values_to = "size") %>% 
  mutate(actor = as.numeric(str_sub(actor,2,-1)),
         effect = factor(effect, levels = as.character(unique(effect))))

rel_importance_actor_w2 <- as.data.frame(rel_importance_actor_w2/D)
rel_importance_actor_w2$effect <- factor(RI_K1$effectNames, levels = RI_K1$effectNames)
rel_importance_actor_w2 <- rel_importance_actor_w2 %>% 
  pivot_longer(!effect, names_to = "actor", values_to = "size") %>% 
  mutate(actor = as.numeric(str_sub(actor,2,-1)),
         effect = factor(effect, levels = as.character(unique(effect))))

rel_importance_actor_w3 <- as.data.frame(rel_importance_actor_w3/D)
rel_importance_actor_w3$effect <- factor(RI_K1$effectNames, levels = RI_K1$effectNames)
rel_importance_actor_w3 <- rel_importance_actor_w3 %>% 
  pivot_longer(!effect, names_to = "actor", values_to = "size") %>% 
  mutate(actor = as.numeric(str_sub(actor,2,-1)),
         effect = factor(effect, levels = as.character(unique(effect))))

#piechart by wave
#png(filename = "Pies_RI_K1.png", width = 35, height = 15, units = "cm", res = 300)

pies <- 
ggplot(rel_importance_K1, aes(x="", y=size, fill=effect))+
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0, direction = -1)+
  scale_fill_manual(values=unname(cols25()))+
  labs(x="",y="") +
  theme_minimal()+
  theme(panel.grid = element_blank())+
  facet_grid(.~wave)+
  theme(legend.position = "bottom",
        axis.ticks = element_blank(), 
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        strip.text.x = element_text(size = 14))

#dev.off()


#barchart by wave and actor

#png(filename = "Bars_RI_K1_w1.png", width = 25, height = 15, units = "cm", res = 300)

bars_actor_K1_w1 <- 
ggplot(rel_importance_actor_w1, aes(x=actor, y=size, fill=effect)) +
  geom_bar(stat="identity", width=.8)+
  scale_fill_manual(values=unname(cols25()))+#, labels = as.factor(as.character(str_sub(rel_importance_actor_w1$effect, 6,-1))))+
  ylab("relative importance") +
  ggtitle("wave1")+
  scale_x_continuous("actor", labels = as.character(rel_importance_actor_w1$actor), breaks = rel_importance_actor_w1$actor)+
  theme_minimal()+
  theme(legend.position = "none")

bars_actor_K1_w2 <- 
ggplot(rel_importance_actor_w2, aes(x=actor, y=size, fill=effect)) +
  geom_bar(stat="identity", width=.8)+
  scale_fill_manual(values=unname(cols25()))+#, labels = as.factor(as.character(str_sub(rel_importance_actor_w2$effect, 6,-1))))+
  ylab("relative importance") +
  ggtitle("wave2")+
  scale_x_continuous("actor", labels = as.character(rel_importance_actor_w2$actor), breaks = rel_importance_actor_w2$actor)+
  theme_minimal()+
  theme(legend.position = "none")

bars_actor_K1_w3 <- 
ggplot(rel_importance_actor_w3, aes(x=actor, y=size, fill=effect)) +
  geom_bar(stat="identity", width=.8)+
  scale_fill_manual(values=unname(cols25()))+#, labels = as.factor(as.character(str_sub(rel_importance_actor_w3$effect, 6,-1))))+
  ylab("relative importance") +
  ggtitle("wave3")+
  scale_x_continuous("actor", labels = as.character(rel_importance_actor_w3$actor), breaks = rel_importance_actor_w3$actor)+
  theme_minimal()+
  theme(legend.position = "none")


#png(filename = "Bars_RI_K1_allwaves.png", width = 35, height = 50, units = "cm", res = 300)

grid.arrange(bars_actor_K1_w1, bars_actor_K1_w2, bars_actor_K1_w3, nrow = 3) # +pies alternatively

#dev.off()


#create table with standard deviations
rel_importance_sd_w1_K1 <- rel_importance_actor_w1 %>% 
  group_by(effect) %>% 
  mutate(averageRI.w1 = mean(size),
         sdRI.w1 = sd(size)) %>% 
  slice(1) %>% 
  select(-actor,-size)

rel_importance_sd_w2_K1 <- rel_importance_actor_w2 %>% 
  group_by(effect) %>% 
  mutate(averageRI.w2 = mean(size),
         sdRI.w2 = sd(size)) %>% 
  slice(1) %>% 
  select(-actor,-size) %>% 
  ungroup %>% 
  mutate(effect = rel_importance_sd_w1_K1$effect)


rel_importance_sd_w3_K1 <- rel_importance_actor_w3%>% 
  group_by(effect) %>% 
  mutate(averageRI.w3 = mean(size),
         sdRI.w3 = sd(size)) %>% 
  slice(1) %>% 
  select(-actor,-size) %>% 
  ungroup %>% 
  mutate(effect = rel_importance_sd_w1_K1$effect)

rel_importance_sd_K1 <- full_join(rel_importance_sd_w1_K1,rel_importance_sd_w2_K1, by = "effect") %>%
  left_join(.,rel_importance_sd_w3_K1, by = "effect")

```

```{r}
#  cohort 2
# RI_K2 <-sienaRI(Data_K2, saomResults_K2[[1]]) 
# plot(RI_K2, addPieChart = T) # plot only for the first imputation


rel_importance_imp_w1_se_wi <- data.frame(matrix(nrow = 13,ncol = D))
rel_importance_imp_w2_se_wi <- data.frame(matrix(nrow = 13,ncol = D))
rel_importance_imp_w3_se_wi <- data.frame(matrix(nrow = 13,ncol = D))

rel_importance_impwise_w1 <- data.frame(matrix(nrow = 13,ncol = D))
rel_importance_impwise_w2 <- data.frame(matrix(nrow = 13,ncol = D))
rel_importance_impwise_w3 <- data.frame(matrix(nrow = 13,ncol = D))

for (i in 1:D) {
  if (i == 1) {
    
    RI_K2 <-sienaRI(Data_K2, saomResults_K2[[i]])
    #average expected relative importance over all actors summing over all imputations
    rel_importance_K2 <- as.matrix(as.data.frame(RI_K2$expectedRI, col.names = c("wave1","wave2","wave3")))
    
    #average expected relative importance over all actors by each imputation
    rel_importance_impwise_w1[,i] <- RI_K2$expectedRI[[1]]
    rel_importance_impwise_w2[,i] <- RI_K2$expectedRI[[2]]
    rel_importance_impwise_w3[,i] <- RI_K2$expectedRI[[3]]
    
    #relative importance of individual actor decisions
    rel_importance_actor_w1 <- as.matrix(as.data.frame(RI_K2$RIActors[[1]]))
    rel_importance_actor_w2 <- as.matrix(as.data.frame(RI_K2$RIActors[[2]]))
    rel_importance_actor_w3 <- as.matrix(as.data.frame(RI_K2$RIActors[[3]]))
    
    #within imputation standard error
    rel_importance_imp_w1_se_wi[,i] <- apply(as.data.frame(t(RI_K2$RIActors[[1]])),2, std.error) #sd or std.error
    rel_importance_imp_w2_se_wi[,i] <- apply(as.data.frame(t(RI_K2$RIActors[[2]])),2, std.error) #sd or std.error
    rel_importance_imp_w3_se_wi[,i] <- apply(as.data.frame(t(RI_K2$RIActors[[3]])),2, std.error) #sd or std.error
    #rel_importance_imp_w2_se_wi[,i] <- apply(as.data.frame(t(RI_K1$RIActors[[2]])),2, sd) /sqrt(ncol(as.data.frame(RI_K1$RIActors[[2]])))
    #rel_importance_imp_w3_se_wi[,i] <- apply(as.data.frame(t(RI_K1$RIActors[[3]])),2, sd) /sqrt(ncol(as.data.frame(RI_K1$RIActors[[3]])))
    
  } else {
    
    RI_K2 <-sienaRI(Data_K2, saomResults_K2[[i]])
    #average expected relative importance over all actors; summing up over all imputations
    rel_importance_K2 <- rel_importance_K2 + as.matrix(as.data.frame(RI_K2$expectedRI, col.names = c("wave1","wave2","wave3")))
    
    #average expected relative importance over all actors by each imputation
    rel_importance_impwise_w1[,i] <- RI_K2$expectedRI[[1]]
    rel_importance_impwise_w2[,i] <- RI_K2$expectedRI[[2]]
    rel_importance_impwise_w3[,i] <- RI_K2$expectedRI[[3]]
    
    #relative importance of individual actor decisions; summing over all imputations
    rel_importance_actor_w1 <- rel_importance_actor_w1 + as.matrix(as.data.frame(RI_K2$RIActors[[1]]))
    rel_importance_actor_w2 <- rel_importance_actor_w2 + as.matrix(as.data.frame(RI_K2$RIActors[[2]]))
    rel_importance_actor_w3 <- rel_importance_actor_w3 + as.matrix(as.data.frame(RI_K2$RIActors[[3]]))
    
    #within imputation standard error
    rel_importance_imp_w1_se_wi[,i] <- apply(as.data.frame(t(RI_K2$RIActors[[1]])),2, std.error) #sd or std.error
    rel_importance_imp_w2_se_wi[,i] <- apply(as.data.frame(t(RI_K2$RIActors[[2]])),2, std.error) #sd or std.error
    rel_importance_imp_w3_se_wi[,i] <- apply(as.data.frame(t(RI_K2$RIActors[[3]])),2, std.error) #sd or std.error
   
    
  }
}

rel_importance_imp_se_final <- data.frame(matrix(nrow = 13, ncol = 0))
rownames(rel_importance_imp_se_final) <- rownames(rel_importance_actor_w1)
#within imputation standard error: average over imputations
rel_importance_imp_se_final$w1_se_wi <- rowSums(rel_importance_imp_w1_se_wi^2)/D
rel_importance_imp_se_final$w2_se_wi <- rowSums(rel_importance_imp_w2_se_wi^2)/D
rel_importance_imp_se_final$w3_se_wi <- rowSums(rel_importance_imp_w3_se_wi^2)/D

#between imputation standard error
rel_importance_imp_w1_se_bi <- rowSums((rel_importance_impwise_w1 - rowMeans(rel_importance_impwise_w1))^2) / (D-1)
rel_importance_imp_w2_se_bi <- rowSums((rel_importance_impwise_w2 - rowMeans(rel_importance_impwise_w2))^2) / (D-1)
rel_importance_imp_w3_se_bi <- rowSums((rel_importance_impwise_w3 - rowMeans(rel_importance_impwise_w3))^2) / (D-1)

rel_importance_imp_se_final$w1_se_bi <- rel_importance_imp_w1_se_bi
rel_importance_imp_se_final$w2_se_bi <- rel_importance_imp_w2_se_bi
rel_importance_imp_se_final$w3_se_bi <- rel_importance_imp_w3_se_bi

#total standard error
rel_importance_imp_se_final$w1_se_total <- sqrt(rel_importance_imp_se_final$w1_se_wi + rel_importance_imp_se_final$w1_se_bi + (rel_importance_imp_se_final$w1_se_bi / D))
rel_importance_imp_se_final$w2_se_total <- sqrt(rel_importance_imp_se_final$w2_se_wi + rel_importance_imp_se_final$w2_se_bi + (rel_importance_imp_se_final$w2_se_bi / D))
rel_importance_imp_se_final$w3_se_total <- sqrt(rel_importance_imp_se_final$w3_se_wi + rel_importance_imp_se_final$w3_se_bi + (rel_importance_imp_se_final$w3_se_bi / D))

rel_importance_imp_se_final_K2 <- rel_importance_imp_se_final %>% 
  select(ends_with("total"))


rel_importance_K2 <- as.data.frame(rel_importance_K2/D)
rel_importance_K2$effect <- factor(c("outdegree (density)", "reciprocity", "triadic closure (GWESP FF, alpha =1.38)", "indegree - popularity (sqrt)", "indegree - activity (sqrt)",
                    "outdegree - activity (sqrt)", "out-isolates (students nominating nobody)", "same statistics tutorial group", "same introduction to science tutorial group",
                    "both tutorial groups in common", "female receiver", "female sender", "same gender")) #, levels = RI_K2$effectNames)
rel_importance_K2 <- rel_importance_K2 %>%
  pivot_longer(!effect, names_to = "wave", values_to = "size") %>% 
  mutate(effect = factor(effect, levels = as.character(unique(effect))))

rel_importance_actor_w1 <- as.data.frame(rel_importance_actor_w1/D) 
rel_importance_actor_w1$effect <- factor(RI_K2$effectNames, levels = RI_K2$effectNames)
rel_importance_actor_w1 <- rel_importance_actor_w1 %>% 
  pivot_longer(!effect, names_to = "actor", values_to = "size") %>% 
  mutate(actor = as.numeric(str_sub(actor,2,-1)),
         effect = factor(effect, levels = as.character(unique(effect))))

rel_importance_actor_w2 <- as.data.frame(rel_importance_actor_w2/D)
rel_importance_actor_w2$effect <- factor(RI_K2$effectNames, levels = RI_K2$effectNames)
rel_importance_actor_w2 <- rel_importance_actor_w2 %>% 
  pivot_longer(!effect, names_to = "actor", values_to = "size") %>% 
  mutate(actor = as.numeric(str_sub(actor,2,-1)),
         effect = factor(effect, levels = as.character(unique(effect))))

rel_importance_actor_w3 <- as.data.frame(rel_importance_actor_w3/D)
rel_importance_actor_w3$effect <- factor(RI_K2$effectNames, levels = RI_K2$effectNames)
rel_importance_actor_w3 <- rel_importance_actor_w3 %>% 
  pivot_longer(!effect, names_to = "actor", values_to = "size") %>% 
  mutate(actor = as.numeric(str_sub(actor,2,-1)),
         effect = factor(effect, levels = as.character(unique(effect))))

#piechart by wave
#png(filename = "Pies_RI_K2.png", width = 25, height = 15, units = "cm", res = 300)

pies <- 
  ggplot(rel_importance_K2, aes(x="", y=size, fill=effect)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0, direction = -1)+
  scale_fill_manual(values=unname(cols25())) +
  labs(x="",y="") +
  theme_minimal()+
  theme(panel.grid = element_blank())+
  facet_grid(.~wave)+
  theme(legend.position = "bottom",
        axis.ticks = element_blank(), 
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        strip.text.x = element_text(size = 14))

#dev.off()


#barchart by wave and actor

#png(filename = "Bars_RI_K2_w1.png", width = 25, height = 15, units = "cm", res = 300)

bars_actor_K2_w1 <- 
  ggplot(rel_importance_actor_w1, aes(x=actor, y=size, fill=effect)) +
  geom_bar(stat="identity", width=.8)+
  scale_fill_manual(values=unname(cols25()), labels = as.factor(as.character(str_sub(rel_importance_actor_w1$effect, 6,-1))))+
  ylab("relative importance") +
  ggtitle("wave1")+
  scale_x_continuous("actor", labels = as.character(rel_importance_actor_w1$actor), breaks = rel_importance_actor_w1$actor)+
  theme_minimal()+
  theme(legend.position = "none")

bars_actor_K2_w2 <- 
  ggplot(rel_importance_actor_w2, aes(x=actor, y=size, fill=effect)) +
  geom_bar(stat="identity", width=.8)+
  scale_fill_manual(values=unname(cols25()), labels = as.factor(as.character(str_sub(rel_importance_actor_w2$effect, 6,-1))))+
  ylab("relative importance") +
  ggtitle("wave2")+
  scale_x_continuous("actor", labels = as.character(rel_importance_actor_w2$actor), breaks = rel_importance_actor_w2$actor)+
  theme_minimal()+
  theme(legend.position = "none")

bars_actor_K2_w3 <- 
  ggplot(rel_importance_actor_w3, aes(x=actor, y=size, fill=effect)) +
  geom_bar(stat="identity", width=.8)+
  scale_fill_manual(values=unname(cols25()), labels = as.factor(as.character(str_sub(rel_importance_actor_w3$effect, 6,-1))))+
  ylab("relative importance") +
  ggtitle("wave3")+
  scale_x_continuous("actor", labels = as.character(rel_importance_actor_w3$actor), breaks = rel_importance_actor_w3$actor)+
  theme_minimal()+
  theme(legend.position = "none")


#png(filename = "Bars_RI_K2_allwaves.png", width = 35, height = 50, units = "cm", res = 300)

grid.arrange(bars_actor_K2_w1, bars_actor_K2_w2, bars_actor_K2_w3, nrow = 3) # +pies alternatively

#dev.off()


#create table with standard deviations
rel_importance_sd_w1_K2 <- rel_importance_actor_w1 %>% 
  group_by(effect) %>% 
  mutate(averageRI.w1 = mean(size),
         sdRI.w1 = sd(size)) %>% 
  slice(1) %>% 
  select(-actor,-size)

rel_importance_sd_w2_K2 <- rel_importance_actor_w2 %>% 
  group_by(effect) %>% 
  mutate(averageRI.w2 = mean(size),
         sdRI.w2 = sd(size)) %>% 
  slice(1) %>% 
  select(-actor,-size)

rel_importance_sd_w3_K2 <- rel_importance_actor_w3%>% 
  group_by(effect) %>% 
  mutate(averageRI.w3 = mean(size),
         sdRI.w3 = sd(size)) %>% 
  slice(1) %>% 
  select(-actor,-size)

rel_importance_sd_K2 <- left_join(rel_importance_sd_w1_K2,rel_importance_sd_w2_K2, by = "effect") %>%
  left_join(.,rel_importance_sd_w3_K2, by = "effect")
```

```{r}
#bars as alternative to pies on wave level averaged over all actors and imputations
rel_importance_K2 <- rel_importance_K2 %>% mutate(cohort = "hybrid\ncohort")
rel_importance_K1 <- rel_importance_K1 %>% mutate(cohort = "lockdown\ncohort")
rel_importance_both <- rbind(rel_importance_K1, rel_importance_K2) %>% 
  mutate(cohort = factor(cohort, levels = c("lockdown\ncohort","hybrid\ncohort")))
  

bars_both <- 
  ggplot(rel_importance_both, aes(x="", y=size, fill=rev(effect))) +
  geom_bar(stat="identity", width=0.5) +
  coord_flip()+
  #coord_polar("y", start=0, direction = -1)+
  scale_fill_manual(values=unname(cols25()[13:1]),
                    labels= rev(levels(rel_importance_both$effect))) +
  labs(x="",y="") +
  theme_minimal()+
  theme(panel.grid = element_blank())+
  facet_grid(cohort ~ wave, switch = "y")+
  guides(fill = guide_legend(reverse=T, title = "Effect"))+
  theme(legend.position = "bottom",
        #strip.text.x.bottom = element_text(angle = 0),
        axis.ticks = element_blank(), 
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        strip.text.y = element_text(size = 12),
        strip.text.x = element_text(size = 14))


#png(filename = "Pies_as_Bars_RI_K1K2_allwaves.png", width = 35, height = 8, units = "cm", res = 300)

bars_both

#dev.off()



```


# Compare cohorts 

```{r}
colnames(rel_importance_imp_se_final_K1) <- c("wave1","wave2","wave3")
rel_importance_imp_se_final_K1 <- rel_importance_imp_se_final_K1 %>% 
  mutate(effect = factor(c("outdegree (density)", "reciprocity", "triadic closure (GWESP FF, alpha =1.38)", "indegree - popularity (sqrt)", "indegree - activity (sqrt)",
                    "outdegree - activity (sqrt)", "out-isolates (students nominating nobody)", "same statistics tutorial group", "same introduction to science tutorial group",
                    "both tutorial groups in common", "female receiver", "female sender", "same gender"))) %>% 
  pivot_longer(cols = c("wave1","wave2","wave3"), names_to = "wave",values_to = "pooled_se")

colnames(rel_importance_imp_se_final_K2) <- c("wave1","wave2","wave3")
rel_importance_imp_se_final_K2 <- rel_importance_imp_se_final_K2 %>% 
  mutate(effect = factor(c("outdegree (density)", "reciprocity", "triadic closure (GWESP FF, alpha =1.38)", "indegree - popularity (sqrt)", "indegree - activity (sqrt)",
                    "outdegree - activity (sqrt)", "out-isolates (students nominating nobody)", "same statistics tutorial group", "same introduction to science tutorial group",
                    "both tutorial groups in common", "female receiver", "female sender", "same gender"))) %>% 
  pivot_longer(cols = c("wave1","wave2","wave3"), names_to = "wave",values_to = "pooled_se")
```

```{r}
K1_RI_se <- left_join(rel_importance_K1, rel_importance_imp_se_final_K1, by = c("wave", "effect")) %>% 
  mutate(cohort = "K1",
         effect = as.factor(effect)) 

K2_RI_se <- left_join(rel_importance_K2, rel_importance_imp_se_final_K2, by = c("wave", "effect")) %>% 
  mutate(cohort = "K2",
         effect = as.factor(effect)) 

#for the visualization the 83.4 conf. Intervalls are used because they resemble 95% best for group comparisons
qnorm(1-(1-0.834)/2)

both_cohorts_RI_se <- rbind(K1_RI_se, K2_RI_se)

both_cohorts_RI_se_cohort <- left_join(K1_RI_se,K2_RI_se, by = c("wave", "effect"), suffix = c(".k1", ".k2")) %>% 
  mutate(lower.k1 = size.k1 -1.385*pooled_se.k1,
         upper.k1 = size.k1 +1.385*pooled_se.k1,
         lower.k2 = size.k2 -1.385*pooled_se.k2,
         upper.k2 = size.k2 +1.385*pooled_se.k2) %>% 
  mutate(maximum = if_else(upper.k1>upper.k2,upper.k1,upper.k2)) %>% 
  arrange(wave) %>% 
  mutate(z_value = (size.k1 - size.k2) / sqrt((pooled_se.k1)^2 + (pooled_se.k2)^2),
         p_value =round(pnorm(abs(z_value), mean = 0, sd = 1, lower.tail = F), digits = 4),
         sig = if_else(p_value < 0.001, "***", #0.1%
                       if_else(p_value < 0.01, "**", #1%
                               if_else(p_value < 0.05, "*", #5%
                                       "n.s."))),
         p_value_ttest = round(pt(-abs(z_value), df=(((42+66)/2)-2), lower.tail = TRUE),3),
         sig_ttest = if_else(p_value_ttest < 0.001, "***", #0.1%
                       if_else(p_value_ttest < 0.01, "**", #1%
                               if_else(p_value_ttest < 0.05, "*", #5%
                                       "n.s."))))
```


```{r}
#print table about RI comparison for appendix
both_cohorts_RI_se_cohort_print <- both_cohorts_RI_se_cohort %>% 
  mutate(est_se_K1 = paste0(as.character(format(round(size.k1,3)), nsmall = 3)," (",as.character(format(round(pooled_se.k1,3)), nsmall = 3),")"),
         est_se_K2 = paste0(as.character(format(round(size.k2,3)), nsmall = 3)," (",as.character(format(round(pooled_se.k2,3)), nsmall = 3),")"),
         effect = as.character(effect)) %>% 
  select(effect, wave, est_se_K1,est_se_K2,p_value) %>% 
  mutate(effect = as.character(effect),
         p_value = as.character(format(round(p_value,3))),
         p_value = if_else(p_value == "0.000", "<.001", substr(p_value,2,5))) %>% 
  pivot_wider(names_from = wave, values_from = c(est_se_K1,est_se_K2,p_value)) %>% 
  select(effect, ends_with("wave1"),ends_with("wave2"),ends_with("wave3"))
  
```

```{r}
stargazer(both_cohorts_RI_se_cohort_print, summary = FALSE, title="Testing differences between cohorts Relative Importance",
          rownames = TRUE, type = "html", out = "Results/differences_K1_K2_RI.html")
```



```{r, warning=FALSE}
level_order <- c("outdegree (density)", "reciprocity", "triadic closure (GWESP FF, alpha =1.38)", "indegree - popularity (sqrt)", "indegree - activity (sqrt)",
                    "outdegree - activity (sqrt)", "out-isolates (students nominating nobody)", "same statistics tutorial group", "same introduction to science tutorial group",
                    "both tutorial groups in common", "female receiver", "female sender", "same gender")

both_cohorts_RI_se_reduced <- both_cohorts_RI_se %>%
  filter(effect %in% c("triadic closure (GWESP FF, alpha =1.38)","same statistics tutorial group", "same introduction to science tutorial group", "both tutorial groups in common"))
both_cohorts_RI_se_cohort_reduced <- both_cohorts_RI_se_cohort %>%
  filter(effect %in% c("triadic closure (GWESP FF, alpha =1.38)","same statistics tutorial group", "same introduction to science tutorial group", "both tutorial groups in common"))

plot_compare_reduced <- ggplot(data=both_cohorts_RI_se_reduced,
                               aes(x = factor(effect, level = level_order), y = size, color = cohort), groups = 1)+ 
  geom_point(aes(shape =  cohort),size = 3, position = position_dodge(w = 0.35)) +
  #ylim(0,0.28)+
  scale_y_continuous(limits = c(0,0.28), breaks=c(0,0.05,0.1,0.15,0.2,0.25))+
  ylab("relative importance of effects\naveraged over actors, pooled (D = 50)")+
  scale_x_discrete(labels = c("triadic closure\n(GWESP FF, alpha =1.38)","same statistics\ntutorial group", "same introduction\nto science tutorial group", "both tutorial groups\nin common"))+
  guides(color = guide_legend(override.aes = list(size=10),
                              title = ""),
         shape = guide_legend(override.aes = list(size=10),
                               title = ""))+
  geom_errorbar(data=both_cohorts_RI_se_reduced, # %>%  filter(wave == "wave1"),
                aes(ymin=size-(pooled_se*1.385),ymax=size+(pooled_se*1.385)),
                position = position_dodge(w = 0.35),
                width = 0.4, size = 1,
                show.legend = FALSE) +
  scale_color_manual(values = c("black","#ff0000"), labels = c("lockdown cohort","hybrid cohort"))+
  scale_shape_manual(values = c(19,17),labels = c("lockdown cohort","hybrid cohort"))+
  geom_signif(data = data.frame(wave = c(replicate(4,"wave1"),replicate(4,"wave2"),replicate(4,"wave3"))),
              aes(y_position = both_cohorts_RI_se_cohort_reduced$maximum + 0.025,
                  xmin = c((1:4)-0.15,(1:4)-0.15,(1:4)-0.15),
                  xmax = c((1:4)+0.15,(1:4)+0.15,(1:4)+0.15),
                  group = 1:12,
                  annotations = both_cohorts_RI_se_cohort_reduced$sig, tip_length = 0.02), size=1,textsize=7,
              manual = T,inherit.aes = FALSE)+
  labs(color = "Cohort", shape = "Cohort") +
  facet_wrap(.~wave, ncol = 3)+
  theme_bw() +
  theme(plot.margin = unit(c(1, 1, 4, 3), "lines"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 20),
        axis.text.x = element_text(vjust=0.4, hjust=0.95, angle = 90, size = 20),
        axis.text.y = element_text(size = 20),
        #axis.text.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        axis.ticks = element_blank(),
        legend.position = 'top',
        legend.text = element_text(size = 24),
        strip.text = element_text(size = 20),
        rect = element_rect(fill = "transparent"),
        panel.background = element_rect(fill = "transparent",
                                        colour = NA_character_), # necessary to avoid drawing panel outline
        plot.background = element_rect(fill = "transparent",
                                       colour = NA_character_), # necessary to avoid drawing plot outline
        legend.background = element_rect(fill = "transparent"),
        legend.box.background = element_rect(fill = "transparent",color = "transparent"),
        legend.key = element_rect(fill = "transparent"))

#as.numeric(t(as.matrix(both_cohorts_RI_se_cohort %>% select(upper.k1,upper.k2))))
png(filename = "RI_cohort_compare_reduced83.4_new.png", width = 45, height = 25, units = "cm", res = 300)

plot_compare_reduced

dev.off()
```



```{r}
todaysdate <- format(Sys.Date(),"%y%m%d")
save(list = ls(.GlobalEnv), file = paste0(todaysdate,"_cohort_comparison_environment_",D,"imp.Rdata"))
```

```{r}
sessionInfo()
```