---
title: "5.2_appendix_either tutorial_cohort2"
author: "Judith Gilsbach"
date: "2023-12-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages
```{r}
library(haven)
library(tidyverse)
library(tidygraph)
library(network)
library(igraph)
library(RSiena)
library(knitr)
library(tableHTML)
library(stargazer)
```

# Load environment from after imputation
```{r}
D <- 50 #number of imputations used in environment to load

# load anaylsis data for cohort 2
```


# Define helper functions

```{r}
#Define Function that will hopefully ensure convergence in RSiena (this is from Siena Manual)
siena07ToConvergence <- function(alg, dat, eff, ans0 = NULL, threshold = 0.25,
                                 nodes = 1, ...){
  # parameters are:
  # alg, dat, eff: Arguments for siena07: algorithm, data, effects object.
  # ans0: previous answer, if available; used as prevAns in siena07.
  # threshold: largest satisfactory value
  #            for overall maximum convergence ratio (indicating convergence).
  # nodes: number of processes for parallel processing.
  if (!is.null(ans0)) {
    alg$nsub = 6
  }
  numr <- 0 # number of repetitions
  ans <- siena07(alg, data = dat, effects = eff, prevAns = ans0,
                 nbrNodes = nodes, returnDeps = TRUE,
                 useCluster = (nodes >= 2), ...) # the first run
  repeat {
    save(ans, file = paste("ans",numr,".RData",sep = "")) # to be safe
    numr <- numr + 1         # count number of repeated runs
    tm <- ans$tconv.max      # convergence indicator
    cat(numr, tm,"\n")       # report how far we are
    if (tm < threshold) {break}   # success
    if (tm > 10) {break}     # divergence without much hope
    # of returning to good parameter values
    if (numr > 20) {break}  # now it has lasted too long
    alg$nsub <- 1
    alg$n2start <- 2 * (sum(eff$include) + 7) * 2.52**4
    alg$n3 <- 3000
    if (numr == 1) {alg$firstg <- alg$firstg/5}
    ans <- siena07(alg, data = dat, effects = eff, prevAns = ans,
                   nbrNodes = nodes, returnDeps = TRUE,
                   useCluster = (nodes >= 2),...)
  }
  if (tm > threshold)
  {
    stop("Convergence inadequate.\n")
  }
  ans
}

#Since version 1.2-12, Maximum Likelihood (ML) estimation by Rsiena with returnDeps = TRUE returns an edgelist of the final network at the end of the phase 3 simulation.
#The following function, getNet(), uses this edgelist to impute the data.

getNet <- function(observedNet,edgeList) {
  # observedNet = observed network as adjacency with missing data
  # edgeList = edgelist that is returned by siena07(...)$sims
  observedNet[is.na(observedNet)] <- 0
  for (i in 1:nrow(edgeList)) {
    observedNet[edgeList[i,1],edgeList[i,2]] <- 1
  }
  return(observedNet)
}


```

# Analysis

## Cohort 2 <br> 2021/22
```{r}
#Specify SAOM
saomResults_K2 <- list()

### move to imp if decided to use ###
Female_v <- as.vector(Attributes_K2$Female)
Female2  <- coCovar(as.vector(Female_v),centered=FALSE)


eithertut2 <- coDyadCovar(either_tutorial_K2) #either WiW or Statistics tutorial group shared
  
  for (i in 1:D) {
    cat('Imputation',i,'\n')
    
    relations_K2 <- sienaDependent(array(c(imp_W1_K2[[i]], imp_W2_K2[[i]],
                                      imp_W3_K2[[i]]), dim = c( 66, 66, 3)))
  
    Data_K2  <- sienaDataCreate(relations_K2, Statistik2, WiW2, both_tutorials2, Female2,eithertut2) 
    effectsData_K2 <- getEffects(Data_K2)
    effectsData_K2 <- includeEffects(effectsData_K2,
                                  recip, density,outActSqrt, inPopSqrt, inActSqrt, outIso)
    # effectsData_K2 <- includeEffects(effectsData_K2,  sameX,
    #                               interaction1 =  "Statistik2")
    # effectsData_K2 <- includeEffects(effectsData_K2,  sameX,
    #                               interaction1 =  "WiW2")
    # effectsData_K2 <- includeEffects(effectsData_K2,  sameX,
    #                               interaction1 =  "both_tutorials2")
    effectsData_K2 <- includeEffects(effectsData_K2, X, name = "relations_K2",
                                     interaction1 = "eithertut2")
    
    effectsData_K2 <- setEffect(effectsData_K2, gwespFF, parameter=138)
    
    #Gender
    effectsData_K2 <- includeEffects(effectsData_K2,  sameX,
                                  interaction1 =  "Female2")
    effectsData_K2 <- includeEffects(effectsData_K2,  egoX,
                                  interaction1 =  "Female2")
    effectsData_K2 <- includeEffects(effectsData_K2,  altX,
                                  interaction1 =  "Female2")
    
    #effectsData_K2 <- setEffect(effectsData_K2, outTrunc, parameter=5)
    
    estimation.options_K2 <- sienaAlgorithmCreate(useStdInits = FALSE, seed = 312,
                                               n3 = 1000, maxlike = FALSE, cond = FALSE,
                                               lessMem = FALSE)
    if (i == 1) {
      saomResults_K2[[i]] <- siena07ToConvergence(alg = estimation.options_K2,
                                               dat = Data_K2, eff = effectsData_K2,
                                               threshold = 0.25)#,
                                               #nodes = 2)
    } else {
      saomResults_K2[[i]] <- siena07ToConvergence(alg = estimation.options_K2,
                                               dat = Data_K2, eff = effectsData_K2,
                                               threshold = 0.25,
                                               ans0 = saomResults_K2[[i - 1]])#, 
                                              # nodes = 2)
    }
    save.image('mi_StatSAOM_K2.RData') 
  }

saomResults_K2[[1]]

```

To assess the quality of the model specification collinearity and autocorreltaion are checked and a gof analysis is performed. This can only be done for individual outputs but not for all D iterations at once. Some some will be checked exemplarily. The number in the braces can be changed to which ever iteration you would like to ckeck e.g., [[2]] for the second iteration.
```{r}
#colliearity check
summary(saomResults_K2[[1]]) #collinearity ok, density (ourdegree) und gwesp knapp unter der Grenze

#check for autocorrelation
saomResults_K2[[1]]$ac
```

```{r}
#gof
saom.results.gof_K2 <- list()
saom.results.gof_K2[[1]] <- plot(sienaGOF(saomResults_K2[[1]], varName="relations_K2", OutdegreeDistribution))
saom.results.gof_K2[[2]] <- plot(sienaGOF(saomResults_K2[[1]], varName="relations_K2", IndegreeDistribution))
saom.results.gof_K2[[1]]
saom.results.gof_K2[[2]]
```

The analysis was performed D times, as the network was omputed D times for each wave. Therefore, the analysis results will be pooled by Rubin's rule.
```{r}
#The combined estimate for the parameters is the average of the estimates of the D analyses
rowVar <- function(x) {
  rowSums((x - rowMeans(x))^2)/(dim(x)[2] - 1)
}

npar <- sum(effectsData_K2$include) #amount of parameters included

#create an dataframe with all estimated parameters and standard errors
MIResults_K2 <- as.data.frame(matrix(,npar,(2 * D)))

for (i in 1:D) {
  
  names(MIResults_K2)[i * 2 - 1] <- paste("imp" , "mean", sep = as.character(i))
  names(MIResults_K2)[i * 2] <- paste("imp" , "se", sep = as.character(i))
  MIResults_K2[,i * 2 - 1] <- saomResults_K2[[i]]$theta
  MIResults_K2[,i * 2] <-  sqrt(diag(saomResults_K2[[i]]$covtheta))
}

#Now we get the average covariance structure between the parameters

WDMIs_K2 <- matrix(0,npar,npar)

for (i in 1:D) {
  WDMIs_K2 <- WDMIs_K2 + saomResults_K2[[i]]$covtheta
}

WDMIs_K2 <- (1/D) * WDMIs_K2

#Using Rubin’s Rules we combine the parameters and standard errors and complete the procedure

finalResults_K2 <- as.data.frame(matrix(,npar,2))
names(finalResults_K2) <- c("combinedEstimate", "combinedSE")
rownames(finalResults_K2) <- effectsData_K2$effectName[effectsData_K2$include]
finalResults_K2$combinedEstimate <- rowMeans(MIResults_K2[,seq(1,2*D,2)])
finalResults_K2$combinedSE <- sqrt(diag(WDMIs_K2) + ((D + 1)/D) *
                                  rowVar(MIResults_K2[,seq(1,2*D,2)]))

#Odds Ratios
finalResults_K2$OddsRatio <- exp(finalResults_K2$combinedEstimate)

kable(round(finalResults_K2, 3))

finalResults_rounded_K2 <- as.data.frame(round(finalResults_K2, 3))

MIResults_K2 <- MIResults_K2

#Significance

finalResults_rounded_K2$sig <- NA
finalResults_rounded_K2$sig[(abs(finalResults_rounded_K2$combinedEstimate) - abs(finalResults_rounded_K2$combinedSE)*1.96)>0]<- "*"
finalResults_rounded_K2$sig[(abs(finalResults_rounded_K2$combinedEstimate) - abs(finalResults_rounded_K2$combinedSE)*2.58)>0]<- "**"
finalResults_rounded_K2$sig[(abs(finalResults_rounded_K2$combinedEstimate) - abs(finalResults_rounded_K2$combinedSE)*3.29)>0]<- "***"

#save the model results
stargazer(finalResults_rounded_K2, summary = FALSE, title=paste0("Analysis results cohort 2, 1st wave imputed with stationary SAOM ",D,"imputations"),
          rownames = TRUE, type = "html", out = paste0("Results/SAOM_analysis_results_K2_either_",D,"_imputations.html"))

```

```{r}
todaysdate <- format(Sys.Date(),"%y%m%d")
save(list = ls(.GlobalEnv), file = paste0(todaysdate,"_analysis_cohort2_environment_",D,"imp","_either_tutorial.Rdata"))
```

```{r}
sessionInfo()
```
