---
title: "X_descriptives"
author: "Judith Gilsbach"
date: "2023-12-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages
```{r}
library(haven)
library(tidyverse)
library(tidygraph)
library(network)
library(igraph)
library(RSiena)
library(knitr)
library(tableHTML)
library(stargazer)
library(gridExtra)
library(plotrix)
```

# Load environment from after imputation

## cohort 1 <br/>(2020/21)
```{r}
date_initial <- "241111" #date the initial environment was created in format yymmdd
D <- 50 #number of imputations used in environment to load

load(paste0(date_initial,"_analysis_cohort1_environment_",D,"imp.Rdata"))
rm(list=setdiff(ls(), c("finalResults_K1","finalResults_rounded_K1","imp_W1_K1","imp_W2_K1","imp_W3_K1")))
```

## cohort 2 <br/>(2021/22)
```{r}
date_initial <- "241111" #date the initial environment was created in format yymmdd
D <- 50 #number of imputations used in environment to load

load(paste0(date_initial,"_analysis_cohort2_environment_",D,"imp.Rdata"))
# rm(list=setdiff(ls(), c("finalResults_K1","finalResults_rounded_K1","finalResults_K2","finalResults_rounded_K2",
#                         "date_initial","D",
#                         "imp_W1_K1","imp_W2_K1","imp_W3_K1",,"imp_W1_K2","imp_W2_K2","imp_W3_K2")))
```

## initial environment

```{r}
date_initial <- "240118" #date the initial environment was created in format yymmdd
load(paste0(date_initial,"_initial_environment.Rdata"))
```

# Descriptives

## Define helper functions
```{r}
diag_na <- function(matrix){
  diag(matrix) <- NA
  return(matrix)
} #converts diagonal to NA (loops counted as missing data)

diag_zero <- function(matrix){
  diag(matrix) <- 0
  return(matrix)
} #converts diagonal to zero (loops counted as non existent ties)

impute_zero_no_loop <- function(matrix){
  matrix[is.na(matrix)] <- 0
  diag(matrix) <- NA
  return(matrix)
} #imputes NA with zero (loops counted as missing data)
```

## Degree of Change <br/>(Jaccard Index)

Stability of the network (only fully observed part) over waves. According to Snijders et al 2010: Snijders, T. A. B., van de Bunt, G. G., and Steglich, C. (2010b). Introduction to actorbased
models for network dynamics. Social Networks, 32:44-60.
Values higher than 0.3 are good. Values higher than 0.2 are okay.

### Cohort 1 (2020/21)
```{r}
edges_W1_K1 <- as.vector(diag_na(relation_W1_K1_ma)[-c(1,15,20,21,24,33,34,38,39,40), #delete columns and lines for missing nodes
                                                    -c(1,15,20,21,24,33,34,38,39,40)])
edges_W2_K1 <- as.vector(diag_na(relation_W2_K1_ma)[-c(1,15,20,21,24,33,34,38,39,40),
                                                    -c(1,15,20,21,24,33,34,38,39,40)])
edges_W3_K1 <- as.vector(diag_na(relation_W3_K1_ma)[-c(1,15,20,21,24,33,34,38,39,40), 
                                                    -c(1,15,20,21,24,33,34,38,39,40)])
jaccard_df_K1<- data.frame(edges_W1_K1,edges_W2_K1,edges_W3_K1) %>%
  mutate(N11_W12 = if_else(edges_W1_K1 == 1 & edges_W2_K1 ==1,1,0), #comparing wave 1 and 2
         N01_W12 = if_else(edges_W1_K1 == 0 & edges_W2_K1 ==1,1,0),
         N10_W12 = if_else(edges_W1_K1 == 1 & edges_W2_K1 ==0,1,0),
         N11_W23 = if_else(edges_W2_K1 == 1 & edges_W3_K1 ==1,1,0), #comparing wave 2 and 3
         N01_W23 = if_else(edges_W2_K1 == 0 & edges_W3_K1 ==1,1,0),
         N10_W23 = if_else(edges_W2_K1 == 1 & edges_W3_K1 ==0,1,0)) %>%
  filter(!is.na(N11_W12)) #filter out missings: These are missing because the edges would resemble loops

sum(jaccard_df_K1$N11_W12)
```

### Cohort 2 (2021/22)
```{r}
edges_W1_K2 <- as.vector(diag_na(relation_W1_K2_ma)[-c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64), #delete columns and lines for missing nodes
                                                                     -c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64)])
edges_W2_K2 <- as.vector(diag_na(relation_W2_K2_ma)[-c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64),
                                                                     -c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64)])
edges_W3_K2 <- as.vector(diag_na(relation_W3_K2_ma)[-c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64), 
                                                                     -c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64)])
jaccard_df_K2<- data.frame(edges_W1_K2,edges_W2_K2,edges_W3_K2) %>%
  mutate(N11_W12 = if_else(edges_W1_K2 == 1 & edges_W2_K2 ==1,1,0), #comparing wave 1 and 2
         N01_W12 = if_else(edges_W1_K2 == 0 & edges_W2_K2 ==1,1,0),
         N10_W12 = if_else(edges_W1_K2 == 1 & edges_W2_K2 ==0,1,0),
         N11_W23 = if_else(edges_W2_K2 == 1 & edges_W3_K2 ==1,1,0), #comparing wave 2 and 3
         N01_W23 = if_else(edges_W2_K2 == 0 & edges_W3_K2 ==1,1,0),
         N10_W23 = if_else(edges_W2_K2 == 1 & edges_W3_K2 ==0,1,0)) %>%
  filter(!is.na(N11_W12)) #filter out missings: These are missing because the edges would resemble loops

sum(jaccard_df_K2$N11_W12)
```

## Density

### Cohort 1 (2020/21)
```{r}
density_df_K1 <- data.frame(Possible_relations = c(NA,NA,NA),
                            Present_relations = NA,
                            Density_null_imputation = NA,
                            Reciprocity_observed = NA,
                            Transitivity_observed = NA,
                            Triads_observed_FF = NA,
                            Students_observed = c(38,39,33),
                            Students_total = c(42,42,42),
                            Jaccard_sim_prev = NA #Jaccard similarity with previous wave
                            )

imputation_df_K1 <- data.frame(Possible_relations = c(NA,NA,NA),
                            Present_relations = NA,
                            Absent_relations = NA,
                            Missing_relations = NA,
                            Density_null_imputation = NA,
                            Density_deletion = NA,
                            Average_density_imputation = NA,
                            Students_observed = c(38,39,33),
                            Students_total = c(42,42,42))

# Loops are not considered possible relations and therefore not missing for missing senders.
#density deletion is calculated under deletion of all actors that have been missing in any wave as our analysis method SAOM can only handle cases which are complete in all waves.
density_df_K1$Possible_relations <- length(nodelist_K1)*length(nodelist_K1)-length(nodelist_K1)
imputation_df_K1$Possible_relations <- density_df_K1$Possible_relations

density_df_K1$Present_relations <- c(table(relation_W1_K1_ma, useNA = "always")[2], #wave 1
                                     table(relation_W2_K1_ma, useNA = "always")[2], #wave 2
                                     table(relation_W3_K1_ma, useNA = "always")[2]) #wave 3
imputation_df_K1$Present_relations <- density_df_K1$Present_relations

imputation_df_K1$Absent_relations <- c(table(diag_na(relation_W1_K1_ma), useNA = "always")[1],
                                    table(diag_na(relation_W2_K1_ma), useNA = "always")[1],
                                    table(diag_na(relation_W3_K1_ma), useNA = "always")[1])


imputation_df_K1$Missing_relations <- c(table(diag_zero(relation_W1_K1_ma), useNA = "always")[3],
                                    table(diag_zero(relation_W2_K1_ma), useNA = "always")[3],
                                    table(diag_zero(relation_W3_K1_ma), useNA = "always")[3])
density_df_K1$Density_null_imputation <- c(c(table(impute_zero_no_loop(relation_W1_K1_ma)))[2]/(42*42-42),
                                           c(table(impute_zero_no_loop(relation_W2_K1_ma)))[2]/(42*42-42),
                                           c(table(impute_zero_no_loop(relation_W3_K1_ma)))[2]/(42*42-42))
imputation_df_K1$Density_null_imputation <- density_df_K1$Density_null_imputation

imputation_df_K1$Density_deletion <- c(table(diag_na(relation_W1_K1_ma)[-c(1,15,20,21,24,33,34,38,39,40),-c(1,15,20,21,24,33,34,38,39,40)])[2]/ #delete columns and lines for missing nodes
                                      (((42-10)*(42-10))-(42-10)),
                                    table(diag_na(relation_W2_K1_ma)[-c(1,15,20,21,24,33,34,38,39,40),-c(1,15,20,21,24,33,34,38,39,40)])[2]/
                                      (((42-10)*(42-10))-(42-10)),
                                    table(diag_na(relation_W3_K1_ma)[-c(1,15,20,21,24,33,34,38,39,40),-c(1,15,20,21,24,33,34,38,39,40)])[2]/
                                      (((42-10)*(42-10))-(42-10)))
density_df_K1$Triads_observed_FF <- c(sum(triad.census(relation_W1_K1_gr)[c(6,8,11,14,15,16)]), #values 6,8,11,14,15,16 are all types of triads of type that include A->B->C; FF, see igraph package documentation
                                      sum(triad.census(relation_W2_K1_gr)[c(6,8,11,14,15,16)]),
                                      sum(triad.census(relation_W3_K1_gr)[c(6,8,11,14,15,16)]))


#Average density after imputation needs to be added after imputation
list_K1_W1_imp_density <- list()
list_K1_W2_imp_density <- list()
list_K1_W3_imp_density <- list()
for (i in 1:D) {
  list_K1_W1_imp_density[i] <- table(diag_na(imp_W1_K1[[i]]))[2]/(42*42-42)
  list_K1_W2_imp_density[i] <- table(diag_na(imp_W2_K1[[i]]))[2]/(42*42-42)
  list_K1_W3_imp_density[i] <- table(diag_na(imp_W3_K1[[i]]))[2]/(42*42-42)
}
imputation_df_K1$Average_density_imputation <- c(mean(unlist(list_K1_W1_imp_density)),mean(unlist(list_K1_W2_imp_density)),mean(unlist(list_K1_W3_imp_density)))

density_df_K1$Reciprocity_observed <- c(reciprocity(relation_W1_K1_gr),
                                        reciprocity(relation_W2_K1_gr),
                                        reciprocity(relation_W3_K1_gr))

density_df_K1$Transitivity_observed <- c(transitivity(relation_W1_K1_gr, type = "global"),
                                         transitivity(relation_W2_K1_gr, type = "global"),
                                         transitivity(relation_W3_K1_gr, type = "global"))

density_df_K1$Jaccard_sim_prev <- c(NA,
                                    sum(jaccard_df_K1$N11_W12)/sum(c(jaccard_df_K1$N01_W12,jaccard_df_K1$N10_W12,jaccard_df_K1$N11_W12)),
                                    sum(jaccard_df_K1$N11_W23)/sum(c(jaccard_df_K1$N01_W23,jaccard_df_K1$N10_W23,jaccard_df_K1$N11_W23)))

stargazer(density_df_K1, summary = FALSE, title="Descriptive statistics cohort 1",
           rownames = FALSE, type = "html", out = paste0("Results/descriptive_cohort1.html"))

stargazer(imputation_df_K1, summary = FALSE, title="Descriptive statistics imputation cohort 1",
           rownames = FALSE, type = "html", out = paste0("Results/descriptive_imputation_cohort1.html"))
```

### Cohort 2 (2021/22)
```{r}
density_df_K2 <- data.frame(Possible_relations = c(NA,NA,NA),
                            Present_relations = NA,
                            Density_null_imputation = NA,
                            Reciprocity_observed = NA,
                            Transitivity_observed = NA,
                            Triads_observed_FF = NA,
                            Students_observed = c(58,54,43),
                            Students_total = c(66,66,66),
                            Jaccard_sim_prev = NA #Jaccard similarity with previous wave
                            )

imputation_df_K2 <- data.frame(Possible_relations = c(NA,NA,NA),
                            Present_relations = NA,
                            Absent_relations = NA,
                            Missing_relations = NA,
                            Density_null_imputation = NA,
                            Density_deletion = NA,
                            Average_density_imputation = NA,
                            Students_observed = c(58,54,43),
                            Students_total = c(66,66,66))

# Loops are not considered possible relations and therefore not missing for missing senders.
#density deletion is calculated under deletion of all actors that have been missing in any wave as our analysis method SAOM can only handle cases which are complete in all waves.
density_df_K2$Possible_relations <- length(nodelist_K2)*length(nodelist_K2)-length(nodelist_K2)
imputation_df_K2$Possible_relations <- density_df_K2$Possible_relations

density_df_K2$Present_relations <- c(table(relation_W1_K2_ma, useNA = "always")[2], #wave 1
                                     table(relation_W2_K2_ma, useNA = "always")[2], #wave 2
                                     table(relation_W3_K2_ma, useNA = "always")[2]) #wave 3
imputation_df_K2$Present_relations <- density_df_K2$Present_relations

imputation_df_K2$Absent_relations <- c(table(diag_na(relation_W1_K2_ma), useNA = "always")[1],
                                    table(diag_na(relation_W2_K2_ma), useNA = "always")[1],
                                    table(diag_na(relation_W3_K2_ma), useNA = "always")[1])
imputation_df_K2$Missing_relations <- c(table(diag_zero(relation_W1_K2_ma), useNA = "always")[3],
                                     table(diag_zero(relation_W2_K2_ma), useNA = "always")[3],
                                     table(diag_zero(relation_W3_K2_ma), useNA = "always")[3])
density_df_K2$Density_null_imputation <- c(c(table(impute_zero_no_loop(relation_W1_K2_ma)))[2]/(66*66-66),
                                           c(table(impute_zero_no_loop(relation_W2_K2_ma)))[2]/(66*66-66),
                                           c(table(impute_zero_no_loop(relation_W3_K2_ma)))[2]/(66*66-66))
imputation_df_K2$Density_null_imputation <- density_df_K2$Density_null_imputation

imputation_df_K2$Density_deletion <- c(table(diag_na(relation_W1_K2_ma)[-c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64), #delete columns and lines for missing nodes
                                                                     -c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64)])[2]/
                                      (((66-27)*(66-27))-(66-27)),
                                    table(diag_na(relation_W2_K2_ma)[-c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64),
                                                                     -c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64)])[2]/
                                      (((66-27)*(66-27))-(66-27)),
                                    table(diag_na(relation_W3_K2_ma)[-c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64),
                                                                     -c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64)])[2]/
                                      (((66-27)*(66-27))-(66-27)))
density_df_K2$Triads_observed_FF <- c(sum(triad.census(relation_W1_K2_gr)[c(6,8,11,14,15,16)]), #values 6,8,11,14,15,16 are all types of triads of type that include A->B->C; FF, see igraph package documentation
                                      sum(triad.census(relation_W2_K2_gr)[c(6,8,11,14,15,16)]),
                                      sum(triad.census(relation_W3_K2_gr)[c(6,8,11,14,15,16)]))

#Average density after imputation needs to be added after imputation
list_K2_W1_imp_density <- list()
list_K2_W2_imp_density <- list()
list_K2_W3_imp_density <- list()
for (i in 1:D) {
  list_K2_W1_imp_density[i] <- table(diag_na(imp_W1_K2[[i]]))[2]/(66*66-66)
  list_K2_W2_imp_density[i] <- table(diag_na(imp_W2_K2[[i]]))[2]/(66*66-66)
  list_K2_W3_imp_density[i] <- table(diag_na(imp_W3_K2[[i]]))[2]/(66*66-66)
}
imputation_df_K2$Average_density_imputation <- c(mean(unlist(list_K2_W1_imp_density)),mean(unlist(list_K2_W2_imp_density)),mean(unlist(list_K2_W3_imp_density)))

density_df_K2$Reciprocity_observed <- c(reciprocity(relation_W1_K2_gr),
                                        reciprocity(relation_W2_K2_gr),
                                        reciprocity(relation_W2_K2_gr))

density_df_K2$Transitivity_observed <- c(transitivity(relation_W1_K2_gr, type = "global"),
                                         transitivity(relation_W2_K2_gr, type = "global"),
                                         transitivity(relation_W3_K2_gr, type = "global"))

density_df_K2$Jaccard_sim_prev <- c(NA,
                                    sum(jaccard_df_K2$N11_W12)/sum(c(jaccard_df_K2$N01_W12,jaccard_df_K2$N10_W12,jaccard_df_K2$N11_W12)),
                                    sum(jaccard_df_K2$N11_W23)/sum(c(jaccard_df_K2$N01_W23,jaccard_df_K2$N10_W23,jaccard_df_K2$N11_W23)))


stargazer(density_df_K2, summary = FALSE, title="Descriptive statistics cohort 2",
           rownames = FALSE, type = "html", out = paste0("Results/descriptive_cohort2.html"))

stargazer(imputation_df_K2, summary = FALSE, title="Descriptive statistics imputation cohort 2",
           rownames = FALSE, type = "html", out = paste0("Results/descriptive_imputation_cohort2.html"))
```
### compare densities and degrees

```{r}
degree_denisty_df <- data.frame(ID = 1:66)

#cohort 1
relation_W1_K1_ma_del <- relation_W1_K1_ma[-c(1,15,20,21,24,33,34,38,39,40),-c(1,15,20,21,24,33,34,38,39,40)]
relation_W1_K1_gr_del <- graph.adjacency(relation_W1_K1_ma_del, mode = "directed", diag = FALSE)

relation_W2_K1_ma_del <- relation_W2_K1_ma[-c(1,15,20,21,24,33,34,38,39,40),-c(1,15,20,21,24,33,34,38,39,40)]
relation_W2_K1_gr_del <- graph.adjacency(relation_W2_K1_ma_del, mode = "directed", diag = FALSE)

relation_W3_K1_ma_del <- relation_W3_K1_ma[-c(1,15,20,21,24,33,34,38,39,40),-c(1,15,20,21,24,33,34,38,39,40)]
relation_W3_K1_gr_del <- graph.adjacency(relation_W3_K1_ma_del, mode = "directed", diag = FALSE)

#cohort 2
relation_W1_K2_ma_del <- relation_W1_K2_ma[-c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64), -c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64)]
relation_W1_K2_gr_del <- graph.adjacency(relation_W1_K2_ma_del, mode = "directed", diag = FALSE)

relation_W2_K2_ma_del <- relation_W2_K2_ma[-c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64), -c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64)]
relation_W2_K2_gr_del <- graph.adjacency(relation_W2_K2_ma_del, mode = "directed", diag = FALSE)

relation_W3_K2_ma_del <- relation_W3_K2_ma[-c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64), -c(12,13,14,15,16,17,20,22,25,29,32,33,35,36,37,38,42,44,50,51,53,57,58,59,60,62,64)]
relation_W3_K2_gr_del <- graph.adjacency(relation_W3_K2_ma_del, mode = "directed", diag = FALSE)


#add to df
degree_denisty_df <- left_join(degree_denisty_df, as.data.frame(degree(relation_W1_K1_gr_del, mode = "out")) %>%  mutate(ID = as.numeric(rownames(.))))
degree_denisty_df <- left_join(degree_denisty_df, as.data.frame(degree(relation_W2_K1_gr_del, mode = "out")) %>%  mutate(ID = as.numeric(rownames(.))))
degree_denisty_df <- left_join(degree_denisty_df, as.data.frame(degree(relation_W3_K1_gr_del, mode = "out")) %>%  mutate(ID = as.numeric(rownames(.))))
degree_denisty_df <- left_join(degree_denisty_df, as.data.frame(degree(relation_W1_K2_gr_del, mode = "out")) %>%  mutate(ID = as.numeric(rownames(.))))
degree_denisty_df <- left_join(degree_denisty_df, as.data.frame(degree(relation_W2_K2_gr_del, mode = "out")) %>%  mutate(ID = as.numeric(rownames(.))))
degree_denisty_df <- left_join(degree_denisty_df, as.data.frame(degree(relation_W3_K2_gr_del, mode = "out")) %>%  mutate(ID = as.numeric(rownames(.))))
colnames(degree_denisty_df) <- c("ID", "K1_W1","K1_W2","K1_W3", "K2_W1","K2_W2","K2_W3")

#t_test
t.test(degree_denisty_df$K1_W1,degree_denisty_df$K2_W1, alternative = "two.sided")
t.test(degree_denisty_df$K1_W2,degree_denisty_df$K2_W2, alternative = "two.sided")
t.test(degree_denisty_df$K1_W3,degree_denisty_df$K2_W3, alternative = "two.sided")
```

```{r}
### t-test with p-values from permutation

#wave 1
print("wave1")
t_obs_W1 <- t.test(degree_denisty_df$K1_W1,degree_denisty_df$K2_W1, alternative = "two.sided", var.equal = TRUE)$statistic
t_obs_W1

combined <- c(degree_denisty_df$K1_W1,degree_denisty_df$K2_W1)
n_permutations <- 100000

# Initialize a vector to store permutation t-statistics
perm_t_stats <- numeric(n_permutations)

# Perform permutations
for (i in 1:n_permutations) {
  permuted <- sample(combined) # Shuffle the combined data
  perm_group1 <- permuted[1:length(degree_denisty_df$K1_W1)] # Assign to group1
  perm_group2 <- permuted[(length(degree_denisty_df$K1_W1) + 1):length(permuted)] # Assign to group2
  perm_t_stats[i] <- t.test(perm_group1, perm_group2, var.equal = TRUE)$statistic
}

p_value <- (sum(abs(perm_t_stats) >= abs(t_obs_W1)) + 1) / (n_permutations + 1)
p_value

#wave 2
print("wave2")
t_obs_W2 <- t.test(degree_denisty_df$K1_W2,degree_denisty_df$K2_W2, alternative = "two.sided", var.equal = TRUE)$statistic
t_obs_W2

combined <- c(degree_denisty_df$K1_W2,degree_denisty_df$K2_W2)

# Perform permutations
for (i in 1:n_permutations) {
  permuted <- sample(combined) # Shuffle the combined data
  perm_group1 <- permuted[1:length(degree_denisty_df$K1_W2)] # Assign to group1
  perm_group2 <- permuted[(length(degree_denisty_df$K1_W2) + 1):length(permuted)] # Assign to group2
  perm_t_stats[i] <- t.test(perm_group1, perm_group2, var.equal = TRUE)$statistic
}

p_value <- (sum(abs(perm_t_stats) >= abs(t_obs_W2)) + 1) / (n_permutations + 1)
p_value

#wave 3
print("wave3")
t_obs_W3 <- t.test(degree_denisty_df$K1_W3,degree_denisty_df$K2_W3, alternative = "two.sided", var.equal = TRUE)$statistic
t_obs_W3

combined <- c(degree_denisty_df$K1_W3,degree_denisty_df$K2_W3)

# Perform permutations
for (i in 1:n_permutations) {
  permuted <- sample(combined) # Shuffle the combined data
  perm_group1 <- permuted[1:length(degree_denisty_df$K1_W3)] # Assign to group1
  perm_group2 <- permuted[(length(degree_denisty_df$K1_W3) + 1):length(permuted)] # Assign to group2
  perm_t_stats[i] <- t.test(perm_group1, perm_group2, var.equal = TRUE)$statistic
}

p_value <- (sum(abs(perm_t_stats) >= abs(t_obs_W2)) + 1) / (n_permutations + 1)
p_value
```


```{r}

degree_df_long <- pivot_longer(degree_denisty_df, cols = starts_with("K"), names_to = "cohort_wave", values_to = "outdegree") %>% 
  mutate(cohort = substr(cohort_wave,1,2),
         wave = substr(cohort_wave,4,5)) %>% 
  mutate(cohort = case_match(cohort,
                           "K1" ~ "lockdown cohort",
                           "K2" ~ "hybrid cohort"),
         wave = case_match(wave,
                           "W1" ~ "wave 1",
                           "W2" ~ "wave 2",
                           "W3" ~ "wave 3")) %>% 
  mutate(cohort = factor(cohort, levels = c("lockdown cohort", "hybrid cohort")))

degree_df_summary <- degree_df_long %>% 
  group_by(cohort, wave) %>% 
  summarize(mean_degree = mean(outdegree, na.rm = T)) %>% 
  ungroup() #%>% 
  # mutate(se_degree = c(std.error(degree_denisty_df$K1_W1,na.rm = T),
  #                      std.error(degree_denisty_df$K1_W2,na.rm = T),
  #                      std.error(degree_denisty_df$K1_W3,na.rm = T),
  #                      std.error(degree_denisty_df$K2_W1,na.rm = T),
  #                      std.error(degree_denisty_df$K2_W2,na.rm = T),
  #                      std.error(degree_denisty_df$K2_W3,na.rm = T)))


density_df_summary <- degree_df_summary %>% 
  select(cohort, wave) %>% 
  mutate(density = c(edge_density(relation_W1_K1_gr_del),
                     edge_density(relation_W2_K1_gr_del),
                     edge_density(relation_W3_K1_gr_del),
                     edge_density(relation_W1_K2_gr_del),
                     edge_density(relation_W2_K2_gr_del),
                     edge_density(relation_W3_K2_gr_del)))


```

```{r}
degree_plot <-
ggplot(degree_df_summary, aes(x = wave, y = mean_degree, group = cohort, color = cohort, fill = cohort, shape =cohort)) +
  geom_point(aes(shape = cohort),size = 3, stroke = 1.5) +
  scale_color_manual(values = c("black","#ff0000"), labels = c("lockdown cohort","hybrid cohort"))+
  guides(color = guide_legend(show.legend = F))+
  scale_fill_manual(values = c("black","#ff0000"), labels = c("lockdown cohort","hybrid cohort"))+
  scale_x_discrete(labels = c("start of term", "midterm", "end of term"))+
  geom_line(aes(linetype = cohort),size = 1) +
  #geom_ribbon(aes(ymin = mean_degree - se_degree*1.96, ymax = mean_degree + se_degree*1.96), alpha = 0.2) +
  ylim(0,15)+
  labs(y = "mean outdegree", x = "Wave", fill = "Cohort", color = "Cohort", linetype = "Cohort", shape = "Cohort") +
  theme_bw() +
  theme(plot.margin = unit(c(1, 1, 4, 3), "lines"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 20),
        axis.text.x = element_text(vjust=0, hjust=0.5, angle = 0, size = 20),
        axis.text.y = element_text(size = 18),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        axis.ticks = element_blank(),
        legend.position = 'top',
        legend.text = element_text(size = 18),
        legend.title = element_blank(),
        rect = element_rect(fill = "transparent"),
        panel.background = element_rect(fill = "transparent",
                                        colour = NA_character_), # necessary to avoid drawing panel outline
        plot.background = element_rect(fill = "transparent",
                                       colour = NA_character_), # necessary to avoid drawing plot outline
        legend.background = element_rect(fill = "transparent"),
        #legend.box.background = element_rect(fill = "transparent"),
        legend.key = element_rect(fill = "transparent"))

density_plot <-
ggplot(density_df_summary, aes(x = wave, y = density, group = cohort, color = cohort, fill = cohort)) +
  geom_point(aes(shape = cohort),size = 3, stroke = 1.5) +
    scale_color_manual(values = c("black","#ff0000"), labels = c("lockdown cohort","hybrid cohort"))+
  guides(color = guide_legend(show.legend = F))+
  scale_fill_manual(values = c("black","#ff0000"), labels = c("lockdown cohort","hybrid cohort"))+
  scale_x_discrete(labels = c("start of term", "midterm", "end of term"))+
  geom_line(aes(linetype = cohort),size = 1) +
  ylim(0,0.3)+
  labs(y = "density", x = "wave", fill = "Cohort", color = "Cohort", linetype = "Cohort", shape = "Cohort") +
  theme_bw() +
  theme(plot.margin = unit(c(1, 1, 4, 3), "lines"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 20),
        axis.text.x = element_text(vjust=0, hjust=0.5, angle = 0, size = 20),
        axis.text.y = element_text(size = 18),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.border = element_blank(),
        axis.ticks = element_blank(),
        legend.position = 'top',
        legend.text = element_text(size = 18),
        legend.title = element_blank(),
        rect = element_rect(fill = "transparent"),
        panel.background = element_rect(fill = "transparent",
                                        colour = NA_character_), # necessary to avoid drawing panel outline
        plot.background = element_rect(fill = "transparent",
                                       colour = NA_character_), # necessary to avoid drawing plot outline
        legend.background = element_rect(fill = "transparent"),
        #legend.box.background = element_rect(fill = "transparent"),
        legend.key = element_rect(fill = "transparent"))



```

```{r}
png(filename = "density_cohort_compare2.png", width = 45, height = 17, units = "cm", res = 300)

grid.arrange(density_plot, degree_plot, nrow = 1)

dev.off()
```


### Jaccard Table both Cohorts
```{r}
# Jaccard_similarity <- data.frame(cohort = c("cohort 1", "cohort 2"),
#                                  Jaccard_W12 = NA,
#                                  Jaccard_W23 = NA)
# Jaccard_similarity$Jaccard_W12 <- c(sum(jaccard_df_K1$N11_W12)/sum(c(jaccard_df_K1$N01_W12,jaccard_df_K1$N10_W12,jaccard_df_K1$N11_W12)), #cohort 1
#                                     sum(jaccard_df_K2$N11_W12)/sum(c(jaccard_df_K2$N01_W12,jaccard_df_K2$N10_W12,jaccard_df_K2$N11_W12))) #cohort 2
# Jaccard_similarity$Jaccard_W23 <- c(sum(jaccard_df_K1$N11_W23)/sum(c(jaccard_df_K1$N01_W23,jaccard_df_K1$N10_W23,jaccard_df_K1$N11_W23)), #cohort 1
#                                     sum(jaccard_df_K2$N11_W23)/sum(c(jaccard_df_K2$N01_W23,jaccard_df_K2$N10_W23,jaccard_df_K2$N11_W23))) #cohort 2
# print(Jaccard_similarity)
# 
# stargazer(Jaccard_similarity, summary = FALSE, title="Jaccard similarity between waves for both cohorts",
#           rownames = FALSE, type = "html", out = paste0("Results/descriptive_Jaccard_similarity.html"))
```



### Friends and acquaintances not found

Students were asked in the second wave respectively, how many of their friends and acquaintances in their year they did not find among the portraits i.e., who were in their cohort but did not take part in the study.

```{r}
not_found_K1 <- Welle2_K1 %>%
  select(NW02001a) %>%
  mutate(status =
  case_match(NW02001a, "A1" ~ "I did not find more than 2 friends or acquaintances",
             "A2" ~ "I did not find 2 friends or acquaintances",
             "A3" ~ "I did not find 1 friend or acquaintance",
             "A4" ~ "I found all my friends and acquaintances",
             "A5" ~ "I am not sure"))
table(not_found_K1$status)
```
```{r}
not_found_K2 <- Welle2_K2 %>%
  select(NW02001a) %>%
  mutate(status =
  case_match(NW02001a, "A1" ~ "I did not find more than 2 friends or acquaintances",
             "A2" ~ "I did not find 2 friends or acquaintances",
             "A3" ~ "I did not find 1 friend or acquaintance",
             "A4" ~ "I found all my friends and acquaintances",
             "A5" ~ "I am not sure"))
table(not_found_K2$status)
```

```{r}
not_found_K1_K2 <- data.frame(table(not_found_K1$status),table(not_found_K2$status))[,c(1,2,4)]
colnames(not_found_K1_K2) <- c("status","cohort 1","cohort 2")
print(not_found_K1_K2)

stargazer(not_found_K1_K2, summary = FALSE, title="How many of your acquaintances and friends among your fellow students in the first semester of sociology could you NOT find in the pictures? Cohort 1, asked in second wave",
          rownames = FALSE, type = "html", out = paste0("Results/descriptive_not_found.html"))
```


```{r}
todaysdate <- format(Sys.Date(),"%y%m%d")
save(list = ls(.GlobalEnv), file = paste0(todaysdate,"_descriptives_environment.Rdata"))
```

```{r}
sessionInfo()
```
